---
title: "Marriage License in Toronto"
subtitle: "My subtitle if needed"
author: 
  - Emily Su
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR, @opendatatoronto and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection....



# Data {#sec-mydatasection}

@fig-marriage showcases a Poisson distribution of marriage licenses in Toronto with a lambda of 10 from 2011 to 2024. As we can see that the distribution of marriages stays the same from 2011 to 2020. However, after 2020, there was a significant jump in the number of marriage licenses in Toronto. This indicates that there are more marriage licenses being created per year after the pandemic than prior.  
```{r}
#| label: fig-marriage
#| fig-cap: Poisson Distribution (Lambda 10) of marriage licenses in Toronto from 2011 to 2024.
#| echo: false

data |>
  ggplot(aes(x = date,
             y = marriage_licenses, color = civic_centre)) + geom_point() + labs(x = "Date", y = "Number of Marriage Licenses", color = "Civic Centres")
```



\newpage


# References


